### 2021-04-14 README.Rmd
update images

You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created

@@

![](inst/README/steveproj-1.png)

@@

![](inst/README/steveproj-2.png)

@@

![](inst/README/steveproj-3.png)

>>>>

You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created.

@@

![](http://svmiller.com/images/github-steveproj/steveproj-1.png)

@@

![](http://svmiller.com/images/github-steveproj/steveproj-2.png)

@@

![](http://svmiller.com/images/github-steveproj/steveproj-3.png)
